Do we need detailed demographic data to forecast plant population responses to climate change?

### 2015-06-10 manuscript/manuscript.tex
updates ms with results

At both levels of inference (individual and quadrat), the building
blocks of our population models are vital rate regressions. For
individual level data we fit models for survival, growth, and
recruitment of new individuals for each species. At the quadrat level we
fit a single regression model for population growth. We describe the
statistical models separately since fitting the models required
different approaches. All models contain five climate covariate that we
chose \emph{a priori}: ``water year'' precipitation at \emph{t}-1
(lagppt); fall through spring precipitation at \emph{t}-1 and \emph{t}-2
(ppt1 and ppt2, respectively) and mean spring temperature at \emph{t}-1
and \emph{t}-2 (TmeanSpr1 and TmeanSpr2, respectively), where \emph{t}
is the observation year.

@@

>>>>

At both levels of inference (individual and quadrat), the building
blocks of our population models are vital rate regressions. For
individual level data we fit models for survival, growth, and
recruitment of new individuals for each species. At the quadrat level we
fit a single regression model for population growth. We describe the
statistical models separately since fitting the models required
different approaches. All models contain five climate covariate that we
chose \emph{a priori}: ``water year'' precipitation at \emph{t}-1
(lagppt); fall through spring precipitation at \emph{t}-1 and \emph{t}-2
(ppt1 and ppt2, respectively) and mean spring temperature at \emph{t}-1
and \emph{t}-2 (TmeanSpr1 and TmeanSpr2, respectively), where \emph{t}
is the observation year. We also include interactions among same-year
climate covariates (e.g., ppt1 $\times$ TmeansSpr1) and climate $\times$
size interactions.

@@

\begin{table}[ht]
\centering
\caption{Percent change from equilibrium (temporal median of simulated plant cover) at observed climate relative to a 1\% climate change as forecast by each model type.} 
\begin{tabular}{llrr}
  \hline
Species & Simulation & IPM Change (\%) & QBM Change (\%) \\ 
  \hline
BOGR & ppt & 0.92 & 19.43 \\ 
  BOGR & temp & 12.50 & -93.56 \\ 
  BOGR & ppt+temp & 25.06 & -27.88 \\ 
  HECO & ppt & -6.65 & -9.40 \\ 
  HECO & temp & -6.46 & -10.63 \\ 
  HECO & ppt+temp & -25.72 & -14.27 \\ 
  PASM & ppt & -8.53 & 0.25 \\ 
  PASM & temp & 8.03 & 8.06 \\ 
  PASM & ppt+temp & 8.74 & 1.30 \\ 
  POSE & ppt & 1.71 & -8.99 \\ 
  POSE & temp & 20.06 & -16.80 \\ 
  POSE & ppt+temp & 11.06 & 4.04 \\ 
   \hline
\end{tabular}
\end{table}
